Police Shootings and Racism in America

### 2020-10-18 police_eda.Rmd
adding more eda

@@

```{r race shootings vs population demographics}
most_pop <- tail(names(sort(table(final_eda$city))), 6)

@@

  vic <- temp %>% 
  summarise(total_b = sum(str_count(SubjectRace, "B")), 
            total_w = sum(str_count(SubjectRace, "W")),
            total_l = sum(str_count(SubjectRace, "L")),
            total_a = sum(str_count(SubjectRace, "A")),
            total_o = sum(str_count(SubjectRace, "O")))

  vic <- vic %>%
    t() %>%
    as.data.frame(stringsAsFactors = F) %>%
    rownames_to_column("value") %>%
    `rownames<-`(NULL)

  demo <-

}

vic <- final_eda %>% 
  summarise(total_b = sum(str_count(SubjectRace, "B")), 
            total_w = sum(str_count(SubjectRace, "W")),
            total_l = sum(str_count(SubjectRace, "L")),
            total_a = sum(str_count(SubjectRace, "A")),
            total_o = sum(str_count(SubjectRace, "O")))
vic <- vic %>%
  t() %>%
  as.data.frame(stringsAsFactors = F) %>%
  rownames_to_column("value") %>%
  `rownames<-`(NULL)

pop <- final_eda %>% 
  summarise(total_b = sum())
```

@@

ggsave(filename = "figures/eda1.png", race_count)
ggsave(filename = "figures/eda2.png", race_prop)
```

@@

ggsave(filename = "figures/eda3.png", race_count1)
ggsave(filename = "figures/eda4.png", race_prop1)
```

>>>>

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(reshape2)
```

@@

```{r race shootings vs population demographics}
most_pop <- head(names(sort(table(final_eda$city), decreasing = TRUE)), 4)
i <- 1

@@

  vic <- temp %>% 
  summarise(Black = sum(str_count(SubjectRace, "B")), 
            White = sum(str_count(SubjectRace, "W")),
            Hispanic = sum(str_count(SubjectRace, "L")),
            Asian = sum(str_count(SubjectRace, "A")),
            city_pop_2013 = sum(str_count(SubjectRace, "B")) + sum(str_count(SubjectRace, "W")) + 
              sum(str_count(SubjectRace, "L")) + sum(str_count(SubjectRace, "A")) + 
              sum(str_count(SubjectRace, "O"))
  ) %>% 
    mutate(Black = Black/city_pop_2013, 
           White = White/city_pop_2013,
           Hispanic = Hispanic/city_pop_2013,
           Asian = Asian/city_pop_2013)

  vic <- vic %>%
    t() %>%
    as.data.frame(stringsAsFactors = F) %>%
    rownames_to_column("race") %>%
    `rownames<-`(NULL)

  demo <- temp %>% 
    select(black, white, hispanic, asian, city_pop_2013)  %>% 
    mutate(black = black/city_pop_2013, 
           white = white/city_pop_2013,
           hispanic = hispanic/city_pop_2013,
           asian = asian/city_pop_2013)
  demo <- rename(demo, Black = black, White = white, Hispanic = hispanic, Asian = asian)
  demo <- demo[1,]

  demo <- demo %>%
    t() %>%
    as.data.frame(stringsAsFactors = F) %>%
    rownames_to_column("race") %>%
    `rownames<-`(NULL)
  demo <- rename(demo, V1 = 2)

  temp2 <- merge(vic, demo, by = "race") %>% 
    filter(race != "city_pop_2013")
  temp2 <- rename(temp2, "Shootings" = V1.x, "City-Wide" = V1.y)
  temp2 <- melt(temp2)

  plot <- ggplot(temp2, aes(x = race, y = value, fill = variable)) +
    geom_bar(position = "dodge", stat="identity") + 
    labs(x = "Victim Race", y = "Proportion", title = paste0("Race Demographics of Shooting Victims vs. ", c, " Population in 2013")) +
    theme(legend.text = element_text(size = 8),
          legend.key.size = unit(0.4, "cm"),
          plot.title = element_text(size=10, hjust = 0.5)) + 
    scale_fill_manual(values=c("#D48C7D", "#7DB2D4"))

  ggsave(filename = paste0("figures/cityeda", i, ".png"), plot)

  i <- i + 1
}
```

@@

ggsave(filename = "figures/singleeda1.png", race_count)
ggsave(filename = "figures/singleeda2.png", race_prop)
```

@@

ggsave(filename = "figures/multeda1.png", race_count1)
ggsave(filename = "figures/multeda2.png", race_prop1)
```

### 2020-10-18 submissionii.Rmd
adding more eda

|       There appears to be 1,906 incidents in the final dataset in which there was only one victim, and 148 with multiple victims.

@@

```{r, figures-race, fig.show="hold", out.width="50%", fig.cap="Counts (left) and Proportions (right) of Different Races Across Single Victim Shootings"}
par(mar = c(2, 2, .1, .1))
knitr::include_graphics("figures/eda1.png")
knitr::include_graphics("figures/eda2.png")
```

>>>>

|

```{r, figures-city, fig.show="hold", out.width="22%", fig.cap="Counts (left) and Proportions (right) of Different Races Across Single Victim Shootings"}
par(mar = c(3, 3, .1, .1))
knitr::include_graphics("figures/cityeda1.png")
knitr::include_graphics("figures/cityeda2.png")
knitr::include_graphics("figures/cityeda3.png")
knitr::include_graphics("figures/cityeda4.png")
```

|       Additionally, there appears to be 1,906 incidents in the final dataset in which there was only one victim, and 148 with multiple victims.

@@

```{r, figures-single, fig.show="hold", out.width="50%", fig.cap="Counts (left) and Proportions (right) of Different Races Across Single Victim Shootings"}
par(mar = c(2, 2, .1, .1))
knitr::include_graphics("figures/singleeda1.png")
knitr::include_graphics("figures/singleeda2.png")
```
